Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-26 docs/paper.tex
Added spacing before all references

	This work presents two types of algorithms based on ICTS \cite{sharon2011} that optimally solve MAPFM, and is part of a study in which other algorithms in addition to ICTS were taken as starting points for MAPFM algorithms. Those of the first type exhaustively enumerate matchings and use a variant of ICTS as a subroutine; those of the second type are based on an extension of ICTS itself to support matching, ICTS-m. The properties of both classes of algorithms as well as ICTS more generally are discussed, followed by experiments in which a selection of algorithm variants is compared. Additionally, one exhaustive ICTS algorithm is compared to MAPFM algorithms based on CBM \cite{ma2016}, M*\cite{wagner2011}, A*+OD+ID\cite{standley2010} and EPEA*\cite{goldenberg2014}.

@@

	As discussed in \cite{ma2016}, MAPFM generalizes both MAPF and anonymous MAPF, which is MAPF allowing an agent to move to any goal, a problem that can be solved in polynomial time.
	\section{Solving MAPF with Matching using ICTS} % Your contribution
	\label{section:icts-matching}
	In this section, taking ICTS for MAPF as a starting point, two methods to use ICTS for MAPFM are described. The first method relies on a reduction from MAPFM to repeated MAPF: an optimal solution to MAPFM corresponds to a matching of agents to goals, so by exhaustively enumerating all matchings and solving these as MAPF instances, an optimal solution to the MAPFM instance can be found. In the second method, the ICT search itself is modified to allow an agent $a_j^i$ to be matched to any $g_k^i$.
	\subsection{Increasing Cost Tree Search}
	\label{icts}
	In Increasing Cost Tree Search\cite{sharon2011}, the two-step mapping from path combination to SIC described in Section \ref{mapfm} is reversed to search for a solution with minimal SIC. This is done by searching for cost vectors corresponding to increasing SIC at the top level and searching for non-conflicting path combinations (solutions) for each cost vector at the bottom level.

@@

	All algorithms are implemented in Python 3.9 to avoid performance differences as often seen between interpreted versus compiled languages; however, CBM\cite{baauw2021} in experiment 2 does use an SSP solver implemented in C++ as a subroutine. The comparison in this experiment is more coarse-grained as performance differences are sometimes subtle and could potentially be explained by slight implementation optimizations rather than algorithmic properties.

@@

	\subsection{Experiment 2: Algorithms for MAPFM}
	From the variants discussed and compared above, the Exh+E+B+O variant was selected for comparison with various other algorithms for MAPFM. This results in the following set of algorithms whose performance is shown in Figure \ref{fig:r-probs}.
	\begin{itemize}
		\begin{minipage}{0.45\linewidth}
			\item ICTS with approximate sorted exhaustive matching (Exh+E+B+O)
			\item A*+ID+OD with matching ID and sorted exhaustive matching\cite{bruin2021}
			\item EPEA* with matching ID and sorted exhaustive matching\cite{jong2021}
		\end{minipage}
		\hspace{1cm}
		\begin{minipage}{0.40\linewidth}
			\item M* with sorted exhaustive matching\cite{donszelmann2021}
			\item CBM adapted to use SIC, using the successive shortest path algorithm (SSP) \cite{goldberg1987} as subroutine for solving teams\cite{baauw2021}.
		\end{minipage}
	\end{itemize}
	With exception of CBM, all methods described use a variant of sorted exhaustive matching. This is because from each family of algorithms one of the best performing algorithms was chosen, which always was such an exhaustive method as opposed to a generalization of the base algorithm to MAPFM (ICTS-m in this work). A*+ID+OD and EPEA* also make use of matching ID, which is ID applied to the MAPFM instance using the respective exhaustive algorithm as MAPFM solver. The initial groups are here the teams, which is why in single team scenarios (Subfigures \ref{fig:r-25-1-p},\ref{fig:r-75-1-p}) matching ID has no effect. Hypothetically, matching ID could explain why both A*+ID+OD and EPEA* outperform the methods using just sorted exhaustive matching in maps with 75\% wall and 3 teams (\ref{fig:r-75-3-p}).

>>>>

	This work presents two types of algorithms based on ICTS \cite{sharon2011} that optimally solve MAPFM, and is part of a study in which other algorithms in addition to ICTS were taken as starting points for MAPFM algorithms. Those of the first type exhaustively enumerate matchings and use a variant of ICTS as a subroutine; those of the second type are based on an extension of ICTS itself to support matching, ICTS-m. The properties of both classes of algorithms as well as ICTS more generally are discussed, followed by experiments in which a selection of algorithm variants is compared. Additionally, one exhaustive ICTS algorithm is compared to MAPFM algorithms based on CBM \cite{ma2016}, M* \cite{wagner2011}, A*+OD+ID \cite{standley2010} and EPEA* \cite{goldenberg2014}.

@@

	As discussed in \cite{ma2016}, MAPFM generalizes both MAPF and anonymous MAPF, which is MAPF allowing an agent to move to any goal, a problem that can be solved in polynomial time.
	\section{Solving MAPF with Matching using ICTS} % Your contribution
	\label{section:icts-matching}
	In this section, taking ICTS for MAPF as a starting point, two methods to use ICTS for MAPFM are described. The first method relies on a reduction from MAPFM to repeated MAPF: an optimal solution to MAPFM corresponds to a matching of agents to goals, so by exhaustively enumerating all matchings and solving these as MAPF instances, an optimal solution to the MAPFM instance can be found. In the second method, the ICT search itself is modified to allow an agent $a_j^i$ to be matched to any $g_k^i$.
	\subsection{Increasing Cost Tree Search}
	\label{icts}
	In Increasing Cost Tree Search \cite{sharon2011}, the two-step mapping from path combination to SIC described in Section \ref{mapfm} is reversed to search for a solution with minimal SIC. This is done by searching for cost vectors corresponding to increasing SIC at the top level and searching for non-conflicting path combinations (solutions) for each cost vector at the bottom level.

@@

	All algorithms are implemented in Python 3.9 to avoid performance differences as often seen between interpreted versus compiled languages; however, CBM \cite{baauw2021} in experiment 2 does use an SSP solver implemented in C++ as a subroutine. The comparison in this experiment is more coarse-grained as performance differences are sometimes subtle and could potentially be explained by slight implementation optimizations rather than algorithmic properties.

@@

	\subsection{Experiment 2: Algorithms for MAPFM}
	From the variants discussed and compared above, the Exh+E+B+O variant was selected for comparison with various other algorithms for MAPFM. This results in the following set of algorithms whose performance is shown in Figure \ref{fig:r-probs}.
	\begin{itemize}
		\begin{minipage}{0.45\linewidth}
			\item ICTS with approximate sorted exhaustive matching (Exh+E+B+O)
			\item A*+ID+OD with matching ID and sorted exhaustive matching \cite{bruin2021}
			\item EPEA* with matching ID and sorted exhaustive matching \cite{jong2021}
		\end{minipage}
		\hspace{1cm}
		\begin{minipage}{0.40\linewidth}
			\item M* with sorted exhaustive matching \cite{donszelmann2021}
			\item CBM adapted to use SIC, using the successive shortest path algorithm (SSP) \cite{goldberg1987} as subroutine for solving teams \cite{baauw2021}.
		\end{minipage}
	\end{itemize}
	With exception of CBM, all methods described use a variant of sorted exhaustive matching. This is because from each family of algorithms one of the best performing algorithms was chosen, which always was such an exhaustive method as opposed to a generalization of the base algorithm to MAPFM (ICTS-m in this work). A*+ID+OD and EPEA* also make use of matching ID, which is ID applied to the MAPFM instance using the respective exhaustive algorithm as MAPFM solver. The initial groups are here the teams, which is why in single team scenarios (Subfigures \ref{fig:r-25-1-p},\ref{fig:r-75-1-p}) matching ID has no effect. Hypothetically, matching ID could explain why both A*+ID+OD and EPEA* outperform the methods using just sorted exhaustive matching in maps with 75\% wall and 3 teams (\ref{fig:r-75-3-p}).
